---
title: "research"
output: html_document
date: '2022-05-20'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# loading libraries
library(tidyverse)
library(ggplot2)
library(ggpubr)
```


```{r}
# reading csv file
dietary_csv <- read.csv("Data/dietary-composition-by-country.csv")
```


Research Question 1
# How much FAO i.e. Fats Animal Oil is in Vegetable Oil in Australia that is consumed by people in different year?
```{r}
# filter the data
country_vege_oils <- dietary_csv %>%
  filter(Entity == "Australia")
# selecting particular columns
selection <- country_vege_oils %>% select(Year, Vegetable.Oils..FAO..2017..) 

# arranging in descending order based on Vegetable oil FAO
arrange(selection ,desc(Vegetable.Oils..FAO..2017..))
```


Research Question 2.
# Checking the FAO in maize, rice and wheat over the years in single figure.
```{r}
# plotting Maize FAO on different years
maize_plot <- ggplot(country_vege_oils, aes(x = Year, y = Maize..FAO..2017..)) +
  geom_point()
```

```{r}
# plotting Rice FAO on different years
rice_plot <- ggplot(country_vege_oils, aes(x = Year, y = Rice..FAO..2017..)) +
  geom_point()
```

```{r}
# plotting Wheat FAO on different years
wheat_plot <- ggplot(country_vege_oils, aes(x = Year, y = Wheat..FAO..2017..)) +
  geom_point()
```

```{r}
# joining three plots as one figure
ggarrange(maize_plot, rice_plot, wheat_plot)
```

Conclusion: 
 - Maize and Rice FAO is higher in later years but the wheat growth becomes less in later years in Australia.
 
 - Same as maize and rice, Vegetable FAO is growing in later years in Australia.