---
title: "research"
author: "Wanxin Chen"
output: html_document
date: '2022-05-20'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{r libraries}
library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)
```

# Research questions
Rice consumption vs. latitude and region, 2015


# Data
```{r read_data, echo = FALSE}
Assignment4_data <- read_csv("Data/rice-consumption-vs-latitude.csv")
data_tidy <- Assignment4_data %>%
  filter(Year == 2015)%>%
  rename(`Rice consumption(kg/capita/yr)` = `Rice (Milled Equivalent) - Food supply quantity (kg/capita/yr)`) %>%
  rename(Latitude = `Latitude - lp_lat_abst`)

data_tidy <- data_tidy %>% drop_na(`Rice consumption(kg/capita/yr)`) %>% drop_na(Latitude)
```


# Analysis
```{r table-1}

knitr::kable(
  head(arrange(data_tidy,desc(`Rice consumption(kg/capita/yr)`)),20), caption = 'Top 10 countries with the highest annual per capita consumption of rice in 2015',
  booktabs = TRUE,digits = 2
) %>%
kable_styling(latex_options = c("striped", "hold_position"))
```


```{r fig-1, echo = FALSE, fig.align = "center", fig.width = 7}
ggplot(data = data_tidy, 
aes(x = Latitude,
    y = `Rice consumption(kg/capita/yr)`)) +
 geom_point(aes(colour = Continent)) +
 geom_point(data = data_tidy,
 size = 2,
 shape = 1)+
  theme_bw()+
  ggtitle("Distribution of countries in different geographic regions in terms of Latitude")

```
Table 1 ranks all the Annual per capita consumption of rice in different countries in 2015 in descending order, while Figure 1 plots the distribution by Latitude and the geographical region to which the country belongs.

According to Table 1, the top 5 countries with the largest rice consumption are Bangladesh, Laos, Cambodia, Vietnam,In combination with Figure 1, it is easy to notice the phenomenon that the countries with higher Annual per capita consumption of rice are mainly in the Latitude between0 and 0.4. Also, when looking at the color of the points, it can be seen that the points representing higher rice consumption represent the map areas of Africa and Asia.




